% Chapter 1

%\titleformat{\chapter}{\centering\Huge\bfseries}{Part \,\thechapter\}{1em}{}

%\chapter{Introduction} % Main chapter title

\label{Chapter1} % For referencing the chapter elsewhere, use \ref{Chapter1} 

\lhead{ \emph{Loop Cost}} % This is for the header on each page - perhaps a shortened title

%----------------------------------------------------------------------------------------

\section{Introduction}

1. compile  the source file

clang -O1 -emit-llvm -c loops.c 

2. run tests   

opt -analyze -ds --refgroup=true --cls=64 loops.bc

\section{Implementation}
\subsection{Basic Algorithm}
\begin{lstlisting}

class InstrInfo{
public:
  unsigned pairSize;
  Instruction *instruction;
  unsigned currentLoopLevel;
  std::string controlVariable;
  APInt UpperBound[10];
  unsigned PairLevel[10];//each subscript is at each level
  APInt stride[10];  
  unsigned CacheLineCount;
  bool used;
};
  
std::map<Instruction *, InstrInfo> instrInfoList;

class RefGroupBase {
public:
  Instruction* groupLeader;
  APInt loopCost;
  int CalculateCost();
  std::set<Instruction *> groupList;
};

class RefGroup {
public:
  unsigned currentLoopLevel;
  std::string controlVariable;
  std::vector<RefGroupBase > groupForLoop;
};


APInt totalBound[10];

std::map<unsigned, RefGroup> refGroupResult;

\end{lstlisting}


First, use the project 3 part, to collect the  instruction we need here,
and save the information to map structure  instrInfoList;

then, analysis this structure by using the function depends(),and RefGroup
algorith mentioned in Mckinley's paper, divide the instruction to
different group based on different loop control Variable.


then analysis the instruction in each RefGroup, find the leader.

then use the leader to Calculate the loop cost based on different loop
control Variable.

Finally, output all information to screen.

\subsection{Loop Nest Number} 
Find the outermost loop (no parent) of each loopnest, save it to a
currentLoop, then , find another outermost, check if it is same as the
currentLoop, if same, do nothing, not same, let loopNest++, and make
currentLoop = current outermost loop.

\subsection{Get the variable type} 
Need to know the value type of the array, because different type comes
with different layout size. Int would be 4, and doulbe is 8, which
means a cacheline with size 64 can hold 16 integers but 8 doulbe variable. 
This is one thing we need to notice, if we get a pointer value, we
need to find the element it points to.

\subsection{Get the upperbound}
Upperbound is necessary for a[i][k][k] and a[k][j][k], this kind of
situations. We also need to get all level upperbound in advance.


\subsection{Get the dependence} 
 if two instructions are loopinvariant, then in the same group;
else check the outtermost leveal if existing group Spatial, then check
if group temp based on different loop control variable. when insert a
new instruction, I will check it with the exist loop, if has
dependence, then insert it to the group, after that, check it with the
rest instruction, if connected, insert to the same group.

\subsection{Get the leader}
I use the simple idea, to check the distance in differnt loop level
from outermost to innermost, choose the bigger one to be the leader,
when finishing the iteration, get the leader of the group.

\subsection{Calculate the cost}
check the subscript of the groupleader, if the loop control variable
level equals to the subscript level, and subscript belongs to a same
loop level, then self Spatial exist, Calculate it with
UpperBound*stride/cachelinecount, else, let it be 1, then multiple
this value with the UpperBound in other level.

\subsection{Difficulty}
did not deal with nest loop since use a different method comparing
with project 3, could not work well with some spacial cases.
Still need to familiar with scalar evaluation class.
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------


\begin{flushright}
%Guide written by ---\\
%Sunil Patel: \href{http://www.sunilpatel.co.uk}{www.sunilpatel.co.uk}
\end{flushright}
